% ------
% Career
% ------
\section{Career}

\mySubHeadingListStart


  \mySubHeading
  {Senior Software Engineer}{Feb 2023 -- Present}
  {\faIcon{building} Splash, Inc.}{Remote, Contract, USA}
    \myItemListStart
      \myItem{Implementation of multiple React apps into the legacy code in Coldfusion.}
      \myItem{Collaborate with a dynamic team to design, develop, and optimize scalable backend services and APIs to enhance the gaming experience.}
      \myItem{One of the enginneers responsible for the core gameplay functionality on client side.}
      \myItem{Took responsibility of owning multiple features and their development.}
      \myItem{Actively contribute to code reviews, and sharing knowledge across the team.}
    \myItemListEnd

  \mySubHeading
  {Lead Sofware Engineer}{Feb 2019 -- Feb 2023}
  {\faIcon{building} Alteryx, Data Science and Analytics Automation Platform}{Prague, Czechia}
    \myItemListStart
      \myItem{Experienced two promotions during my tenure at Alteryx, advancing from SE to SSE and finally to Lead Software Engineer.}
      \myItem{Acted as SDM for a team of 8 engineers and one product manager for a 6-month period.}
      \myItem{Represented Prague as part of the frontend guild.}
      \myItem{Played a key role in implementing micro-frontend architecture as one of the engineers.}
      \myItem{Successfully led Alteryx Plans as both an engineer and manager, ensuring on-time product delivery.}
      \myItem{Conducted interviews for new candidates, mentored new hires, and prepared workshops for teams.}
    \myItemListEnd

  \mySubHeading
  {Software Engineer}{Feb 2018 -- Feb 2019}
  {\faIcon{building} Generali, Czech Insurance}{Prague, Czechia}
    \myItemListStart
      \myItem{Refactored old Java code with Angular to NodeJS and React.}
      \myItem{Conducted code reviews and shared knowledge within the team.}
      \myItem{Enforced Test-Driven Development (TDD) practices, maintaining test coverage above 90\%.}
      \myItem{Streamlined code with a significant refactor, adopting a more functional approach.}
      \myItem{Implemented core business logic using Redux and Redux-Sagas.}
    \myItemListEnd

  \mySubHeading
  {Software Engineer}{Jun 2017 -- Feb 2018}
  {\faIcon{building} Betsys, Inc.}{Prague, Czechia}
    \myItemListStart
      \myItem{Member of the frontend architecture group.}
      \myItem{Implemented core game engine for virtual sports.}
      \myItem{Investigated and resolved defects.}
      \myItem{Communicated with team members to discuss project requirements.}
      \myItem{Conducted code reviews.}
    \myItemListEnd

  \mySubHeading
  {Junior Software Developer}{Jun 2016 -- Jun 2017}
  {\faIcon{building} Tipsport, a.s.}{Prague, Czechia}
    \myItemListStart
      \myItem{Implemented a new design component system for the company's app.}
      \myItem{Participated in various meetups focusing on frontend development.}
      \myItem{Collaborated with UX/UI designers to create modern and responsive interfaces for web applications.}
    \myItemListEnd

\mySubHeadingListEnd
